\documentclass[11pt,letterpaper]{article}

\usepackage[margin=0.9in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{array}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.35em}
\linespread{1.08}

\definecolor{heading}{HTML}{1F2937}

\titleformat{\section}
  {\large\bfseries\color{heading}}
  {}
  {0em}
  {}
  [\vspace{0.2em}\titlerule]
\titlespacing*{\section}{0pt}{1.25em}{0.75em}

\setlist[itemize]{
  leftmargin=1.4em,
  itemsep=0.35em,
  topsep=0.2em,
  parsep=0pt
}

\newcommand{\entry}[4]{%
  \begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}X>{\raggedleft\arraybackslash}p{1.45in}@{}}
    \textbf{#1} & #2 \\
    \textit{#3} & #4 \\
  \end{tabularx}
}

\newcommand{\publication}[1]{%
  \hangindent=1.2em
  \hangafter=1
  #1\par\vspace{0.45em}
}

\begin{document}

\begin{center}
  {\LARGE\bfseries Ruichen Yang}\\[0.45em]
  Indiana University Bloomington \;|\;
  \href{mailto:ruicyang@iu.edu}{ruicyang@iu.edu} \;|\;
  \href{https://scholar.google.com/citations?user=i4R9ZRsAAAAJ&hl=en&inst=13098912254855678857}{Google Scholar} \;|\;
  \href{https://mukj1.github.io/}{Homepage}
\end{center}

\section*{Education}

\entry
  {Indiana University Bloomington}
  {08/2026 --}
  {PhD Student, Sport Management}
  {}

\vspace{0.35em}

\entry
  {Beijing Sport University}
  {08/2022 -- 06/2025}
  {Master, Humanities and Social Sciences of Sports}
  {}

\vspace{0.35em}

\entry
  {Beijing Sport University}
  {08/2018 -- 06/2022}
  {Bachelor, Sport Economics and Management}
  {}

\section*{Publications}

\publication{Song, H., Gao, J., Fan, S., \textbf{Yang, R.}, \& Liu, Z. (2025). The influence of immersion on revisit intention: Empirical evidence from tourists at the Beijing Winter Olympic venue ``Snow Ruyi'', \textit{International Journal of Sports Marketing and Sponsorship}, pp. 1--20. \url{https://doi.org/10.1108/IJSMS-07-2025-0344}}

\publication{\textbf{Yang, R.} and Song, H. (2024). The spillover effect of Chinese sportswear brands' relationship quality: a perspective of Confucian yuanfen culture, \textit{International Journal of Sports Marketing and Sponsorship}, Vol. 25 No. 5, pp. 1105--1125. \url{https://doi.org/10.1108/IJSMS-02-2024-0049}}

\section*{Conferences}

\publication{Qian, T. Y., Chen, S., \textbf{Yang, R.}, \& Li, W. (2025, October). Human-AI collaboration in sport marketing research: Harnessing practical AI tools and applications. Presented (75-min panel) at the 2025 Sport Marketing Association (SMA) Conference, Phoenix-Glendale, AZ.}

\publication{\textbf{Yang, R.} and Song, H. (2024, June). The factors influencing domestic sportswear brands' purchase intention: A perspective of self-congruity theory. Oral Presentation at the 10th Asian Pacific Conference of Exercise \& Sports Science (APCESS) 2024, Kaifeng, China.}

\publication{\textbf{Yang, R.} and Song, H. (2024, June). The spillover effect of Chinese sportswear brands' relationship quality: A perspective of Confucian yuanfen culture. Oral Presentation at the 2024 International Chinese Society for Physical Activities and Health (ICSPAH) Annual Conference, Beijing, China.}

\section*{Skills \& Certificate}

\begin{tabularx}{\textwidth}{@{}>{\bfseries}p{0.9in}@{\hspace{0.05in}}p{0.08in}@{\hspace{0.12in}}X@{}}
Computers & : & SPSS, SmartPLS, Python, R \\
Languages & : & Chinese, English \\
Certificate & : & Sports Agent - Level Three by General Administration of Sport of China \\
\end{tabularx}

\section*{Awards}

\begin{itemize}
  \item 2024 Beijing Sport University National Scholarship
  \item 2024 Beijing Sport University First-class Academic Scholarship
  \item 2023 Beijing Sport University Second-class Academic Scholarship
  \item 2022 Beijing Sport University Second-class Academic Scholarship
\end{itemize}

\end{document}
